Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-08 ms.tex
added figure showing two-dimensional histogram of reddening residuals
starting to fix up reddening discussion

While the dust temperature and optical depth maps thus far derived are
useful for making predictions of thermal dust foreground emission, 
estimating optical reddening/extinction is another important application of the
optical depth map. We choose to calibrate to empirically to reddening,
rather than make additional assumptions about the dust grain size distribution
and physics that would be necessary to perform an analytic calculation.

@@

% need 2d histogram figure that is as closely analogous as possible to
% Figure 2 of Eddie's draft at : 
% http://faun.rc.fas.harvard.edu/eschlafly/2dmap/2dmap.pdf

>>>>

While the temperature and optical depth maps thus far derived are
useful for making thermal dust emission foreground predictions, estimating 
optical reddening/extinction is another important application of the 
$\tau_{545}$ map. We calibrate to reddening empirically rather than derive
a relationshp between $\tau_{545}$ and reddening by introducing additional 
assumptions about the dust grain physics and size distribution.

@@

\begin{figure}
\begin{center}
\epsfig{file=ebv_2comp.eps, width=2.5in, angle=90}
\caption{\label{fig:resid} Residuals for best-fit $E(B-V)_{2comp}$ as a 
function of SFD $E(B-V)$.}
\end{center}
\end{figure}

% should eventually try re-making 2d scatterplot figure in python..
